This is an example of article title

### 2025-11-01 paper/paper.tex
Unify inline code to never use lstinline since it is very broken within jlcode
cf. https://github.com/wg030/jlcode/issues/57

The main type for Lie Groups is the \verb|LieGroup{|$\mathbb {F}$\verb|, O, M} <: AbstractLieGroup|, which contains a manifold \verb|M <: AbstractManifold{|$\mathbb F$\verb|}| as well as the group operation \verb| O <: AbstractGroupOperation|, where $\mathbb {F}$ is the set of scalars used in the representation of the manifold, usually \(\mathbb {F} = \mathbb{R}\) and in some cases \(\mathbb {F}\) is the field of complex numbers \(\mathbb{C}\) or the ring of quaternions \(\mathbb H\).

@@

Code~\ref{lst:rod-dynamics} shows functions that calculate the right hand side of the ODE, where \lstinline{E_field} is a function that calculates electric field strength from the point charges at the given point.
The function \lstinline{force_and_torque} calculates the force and torque affecting the rod, while \lstinline{dynamics} converts them to the Lie algebra element can be used by the solver.
\begin{lstlisting}[
    float=tbp,
    language = Julia,
    numbers=left,
    label={lst:rod-dynamics},
    caption={Dynamics of a rod affected by point charges.},
    mathescape
]
function force_and_torque(
        sp::SystemParameters, Fθ, r
    )
    u, u${}_\perp$ = eachrow(Fθ)
    F, $\tau$ = zeros(2), 0.0
    for s in range(-sp.L/2, sp.L/2; length=Nq)
        E = E_field(sp, r .+ s .* u)
        F .+= sp.$\lambda$ * E * (sp.L/(Nq-1))
        $\tau$ += sp.$\lambda$ * s * dot(u${}_\perp$, E) * (sp.L/(Nq-1))
    end
    return F, $\tau$
end
# f((p,θ), (dp,dθ), t) where (p,θ) and (dp,dθ) are
# passed as the first argument, system parameters
# as the second one and time as the last one
function dynamics(state, sp::SystemParameters, t)
    p, dp = state.x
    F, tau = force_and_torque(sp, p.x...)
    a = F ./ sp.M
    c = [tau / sp.Icm, a...]
    ddx = hat(sp.lie_algebra, c, ArrayPartition)
    return ArrayPartition(dp, ddx)
end
\end{lstlisting}

>>>>

The main type for Lie Groups is the \verb|LieGroup{|$\mathbb {F}$\verb|, O, M} <: AbstractLieGroup{|$\mathbb {F}$\verb|, O, M}|, which contains a manifold \verb|M <: AbstractManifold{|$\mathbb F$\verb|}| as well as the group operation \verb| O <: AbstractGroupOperation|, where $\mathbb {F}$ is the set of scalars used in the representation of the manifold, usually \(\mathbb {F} = \mathbb{R}\) and in some cases \(\mathbb {F}\) is the field of complex numbers \(\mathbb{C}\) or the ring of quaternions \(\mathbb H\).

@@

Code~\ref{lst:rod-dynamics} shows functions that calculate the right hand side of the ODE, where \verb|E_field| is a function that calculates electric field strength from the point charges at the given point.
The function \verb|force_and_torque| calculates the force and torque affecting the rod, while \verb|dynamics| converts them to the Lie algebra element can be used by the solver.
\begin{lstlisting}[
    float=tbp,
    language = Julia,
    numbers=left,
    label={lst:rod-dynamics},
    caption={Dynamics of a rod affected by point charges.},
    mathescape
]
function force_and_torque(
        sp::SystemParameters, Fθ, r
    )
    u, u${}_\perp$ = eachrow(Fθ)
    F, $\tau$ = zeros(2), 0.0
    for s in range(-sp.L/2, sp.L/2; length=Nq)
        E = E_field(sp, r .+ s .* u)
        F .+= sp.$\lambda$ * E * (sp.L/(Nq-1))
        $\tau$ += sp.$\lambda$ * s * dot(u${}_\perp$, E) * (sp.L/(Nq-1))
    end
    return F, $\tau$
end
# f((p,θ), (dp,dθ), t) where (p,θ) and (dp,dθ) are
# passed as the first argument, system parameters
# as the second one and time as the last one
function dynamics(state, sp::SystemParameters, t)
    p, dp = state.x
    F, tau = force_and_torque(sp, p.x...)
    a = F ./ sp.M
    c = [tau / sp.Icm, a...]
    ddx = hat(sp.lie_algebra, c, ArrayPartition)
    return ArrayPartition(dp, ddx)
end
\end{lstlisting}
